Ecuador plant species POWO

### 2023-02-27 code/L0/L0_Ecuador_plants_POWO.Rmd
add summary code

# Load required packages
```{r}
library(kewr)
library(dplyr)
```

# Search Plants of the World Online [https://powo.science.kew.org/] for species in Ecuador
## Best to break up request into smaller chunks so R handle it without timing out
```{r}
Ecuador_POWO_page1 <- search_powo(list(distribution="Ecuador"), limit = 5000)
Ecuador_POWO_page2 <- request_next(Ecuador_POWO_page1)
Ecuador_POWO_page3 <- request_next(Ecuador_POWO_page2)
Ecuador_POWO_page4 <- request_next(Ecuador_POWO_page3)
Ecuador_POWO_page5 <- request_next(Ecuador_POWO_page4)
```

# Combine pages
```{r}
Ecuador_POWO <- bind_rows(
  tidy(Ecuador_POWO_page1),
  tidy(Ecuador_POWO_page2),
  tidy(Ecuador_POWO_page3),
  tidy(Ecuador_POWO_page4),
  tidy(Ecuador_POWO_page5)
)
```

@@

>>>>

# Load required packages
```{r}
library(kewr)
library(dplyr)
library(DataExplorer)
library(summarytools)
```

# Search Plants of the World Online [https://powo.science.kew.org/] for species in Ecuador
## Best to break up request into smaller chunks so R handle it without timing out
```{r}
Ecuador_POWO_page1 <- search_powo(list(distribution="Ecuador"), limit = 4000)
Ecuador_POWO_page2 <- request_next(Ecuador_POWO_page1)
Ecuador_POWO_page3 <- request_next(Ecuador_POWO_page2)
Ecuador_POWO_page4 <- request_next(Ecuador_POWO_page3)
Ecuador_POWO_page5 <- request_next(Ecuador_POWO_page4)
Ecuador_POWO_page6 <- request_next(Ecuador_POWO_page5)
```

# Combine pages
```{r}
Ecuador_POWO <- bind_rows(
  tidy(Ecuador_POWO_page1),
  tidy(Ecuador_POWO_page2),
  tidy(Ecuador_POWO_page3),
  tidy(Ecuador_POWO_page4),
  tidy(Ecuador_POWO_page5),
  tidy(Ecuador_POWO_page6)
)
```

@@

```{r}
# using DataExplorer package
plot_str(Ecuador_POWO)
introduce(Ecuador_POWO)
plot_intro(Ecuador_POWO)
plot_missing(Ecuador_POWO)
plot_bar(Ecuador_POWO)
```

```{r}
# using summarytools package
Ecuador_POWO_summary <- dfSummary(Ecuador_POWO, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(Ecuador_POWO_summary, method = "render")
view(Ecuador_POWO_summary, file = file.path(output_path,"Ecuador_POWO_summary.html"))
```
